---
title: DATA 606 Data Project Proposal
author: Nicholas Kunze
---

### Data Preparation

```{r setup, echo=TRUE, results='hide', warning=FALSE, message=FALSE}
# load data
wvs7 <- load("data/WVS_Cross-National_Wave_7_rData_v5_0.rdata")
na_wvs <- subset(wvs7, `WVS_Cross-National_Wave_7_v5_0`$B_COUNTRY_ALPHA == "USA" | `WVS_Cross-National_Wave_7_v5_0`$B_COUNTRY_ALPHA == "CAN")

# Rename columns to be more useful - each question in the master pdf maps to a
# column in the df, joined over q#




```


### Research question 

**You should phrase your research question in a way that matches up with the scope of inference your dataset allows for.**



### Cases 

**What are the cases, and how many are there?**



### Data collection 

**Describe the method of data collection.**



### Type of study 

**What type of study is this (observational/experiment)?**



### Data Source 

**If you collected the data, state self-collected. If not, provide a citation/link.**




### Dependent Variable

**What is the response variable? Is it quantitative or qualitative?**



### Independent Variable(s)




### Relevant summary statistics 

**Provide summary statistics for each the variables. Also include appropriate visualizations related to your research question (e.g. scatter plot, boxplots, etc). This step requires the use of R, hence a code chunk is provided below. Insert more code chunks as needed.**

```{r}

```

